\documentclass[10pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[margin=0.5in,top=0.5in,bottom=0.55in]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks,bookmarks=false,pdfusetitle=false]{hyperref}
\usepackage{parskip}
\usepackage{paracol}
\usepackage{calc}
\usepackage{hyphenat}
\usepackage{needspace}
\usepackage{fancyhdr}

% Disable line-end word hyphenation
\hyphenpenalty=10000
\exhyphenpenalty=10000
\tolerance=1000

% Five close harmonious colors in the teal-emerald family + warm amber + neutrals
\definecolor{c1}{HTML}{064E3B}   % deepest emerald - section headings
\definecolor{c2}{HTML}{115E59}   % deep teal - company names (primary accent)
\definecolor{c3}{HTML}{0D9488}   % medium teal - links, secondary
\definecolor{c4}{HTML}{14B8A6}   % light teal - rule lines, accents
\definecolor{c5}{HTML}{99F6E4}   % pale teal - backgrounds, pills
\definecolor{warm}{HTML}{B45309} % amber - version label, special highlights
% Aliases (keep existing macros working)
\colorlet{accent}{c2}
\colorlet{accentDark}{c1}
\colorlet{accentLight}{c4}
\definecolor{ink}{HTML}{0F172A}
\definecolor{ink2}{HTML}{1E293B}
\definecolor{muted}{HTML}{475569}
\definecolor{mutedLight}{HTML}{94A3B8}
\definecolor{rule}{HTML}{CBD5E1}
\definecolor{pillBg}{HTML}{E6F4F2}
\definecolor{pillText}{HTML}{0F4F4A}
\definecolor{pillBorder}{HTML}{99D4CB}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\linespread{1.04}

% Bullet lists - compact, accent triangle
\setlist[itemize]{leftmargin=11pt,labelsep=5pt,itemsep=1pt,topsep=2pt,parsep=0pt,partopsep=0pt}
\renewcommand{\labelitemi}{{\color{accent}\scriptsize$\blacktriangleright$}}

% Simple letter-spacer fallback (no soul package available)
\newcommand{\so}[1]{#1}

% Main section heading - dark emerald title, double-tone rule (teal + pale)
\newcommand{\cvsection}[1]{%
  \vspace{8pt}%
  {\color{c1}\bfseries\fontsize{12}{14}\selectfont\so{\MakeUppercase{#1}}\hspace{6pt}{\color{c3}$\bullet$}}\\[2pt]%
  {\color{c2}\rule{\linewidth}{0.8pt}}\\[-12pt]%
}

% Sidebar section heading - widow-protected so it doesn't dangle at page-bottom
\newcommand{\sidesection}[1]{%
  \needspace{6\baselineskip}%
  \vspace{9pt}%
  {\color{c1}\bfseries\fontsize{10}{12}\selectfont\so{\MakeUppercase{#1}}}\\[1pt]%
  {\color{c4}\rule{\linewidth}{0.6pt}}\\[3pt]%
  \nopagebreak%
}

% Helpers
\newcommand{\meta}[1]{{\color{muted}\fontsize{8.5}{10}\selectfont #1}}

% Role: company (accent) | position (ink2) | right-aligned dates (muted), all on a single line
% \needspace ensures the title plus several lines of body stay together on one page
% Professional role header: 2-row tabular with proper column alignment.
% Row 1: company (bold accent) | dates (muted, right)
% Row 2: position (warm amber) | location (muted, right)
% Args: {company}{position}{location}{dates}
\newcommand{\role}[4]{%
  \needspace{5\baselineskip}%
  \vspace{15pt}%
  \noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\color{accent}\bfseries\fontsize{12}{14}\selectfont #1} &
    {\color{muted}\fontsize{8.5}{10}\selectfont #4} \\[5pt]
    {\color{warm}\bfseries\fontsize{9.75}{11.5}\selectfont #2} &
    {\color{muted}\fontsize{8.5}{10}\selectfont #3} \\
  \end{tabular*}%
  \par\vspace{6pt}\nopagebreak%
}

% Simpler 2-arg variant for "Earlier roles" header (no position/location split)
\newcommand{\roleSimple}[2]{%
  \needspace{4\baselineskip}%
  \vspace{15pt}%
  \noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
    {\color{accent}\bfseries\fontsize{12}{14}\selectfont #1} &
    {\color{muted}\fontsize{8.5}{10}\selectfont #2} \\
  \end{tabular*}%
  \par\vspace{6pt}\nopagebreak%
}

% Tech line: forced new line, single line (text shrinks if needed via \resizebox)
% Sort items by importance — only headline tech, never wraps to second line
\newcommand{\techline}[1]{%
  \par\vspace{3pt}\noindent%
  \textcolor{c3}{\rule[-1pt]{2pt}{10pt}}\hspace{6pt}%
  {\color{c2}\bfseries\fontsize{8}{10}\selectfont\so{TECH}}\hspace{6pt}%
  {\color{ink2}\fontsize{8.5}{10}\selectfont #1}%
  \par\vspace{6pt}%
}

% Skill group in sidebar
\newcommand{\skillgroup}[2]{%
  {\fontsize{9}{11}\selectfont\textbf{\color{ink}#1}}\\[0pt]%
  {\fontsize{8.5}{11}\selectfont\color{muted} #2}\par\vspace{3pt}%
}

% Contact line item: warm accent label + ink content
\newcommand{\contactitem}[2]{%
  {\fontsize{8.5}{11}\selectfont {\color{c1}\textbf{\so{\MakeUppercase{#1}}}}\,\, {\color{ink}#2}}\par\vspace{2pt}%
}

\setlength{\emergencystretch}{2em}
\columnratio{0.28}
\setlength{\columnsep}{22pt}

\begin{document}

% ===== HEADER =====
% Accent bar on top
\noindent{\color{accent}\rule{\linewidth}{3pt}}\vspace{4pt}\\[-1pt]

\noindent
\begin{minipage}[t]{0.66\linewidth}
\vspace{6pt}
{\fontsize{24}{28}\selectfont\bfseries\color{ink} Mohammad Efazati}\\[5pt]
{\fontsize{12}{15}\selectfont\color{accent}\bfseries Principal DevOps Engineer \,$\cdot$\, Co-Founder of EasyEnv}\\[8pt]
{\fontsize{9.5}{12}\selectfont\color{ink}
20+ years building production infrastructure and engineering teams across 50+ companies. Ran thousands of technical interviews along the way, and now co-founding \href{https://easyenv.io}{\color{accent}\textbf{EasyEnv}}, the hiring platform that interviews engineers on real Linux boxes, AI included.}
\end{minipage}\hfill
\begin{minipage}[t]{0.32\linewidth}
\vspace{6pt}
\raggedleft
\contactitem{Location}{Tullamore, Co. Offaly, Ireland}
\contactitem{Phone}{+353 83 857 4516}
\contactitem{Email}{\href{mailto:mohammad@efazati.org}{mohammad@efazati.org}}
\contactitem{Web}{\href{https://efazati.org}{efazati.org}}
\contactitem{GitHub}{\href{https://github.com/efazati}{github.com/efazati}}
\contactitem{LinkedIn}{\href{https://linkedin.com/in/efazati}{linkedin.com/in/efazati}}
\end{minipage}
\vspace{14pt}

% ===== TWO-COLUMN BODY =====
\begin{paracol}{2}

% ----- LEFT SIDEBAR -----
\fontsize{9}{11.5}\selectfont

\sidesection{Programming}
\skillgroup{Expert}{Python (10+ years)}
\skillgroup{Proficient}{Go, Bash}
\skillgroup{Familiar}{Rust, Node.js, PHP, JavaScript}

\sidesection{Cloud \& Infrastructure}
\skillgroup{Cloud}{GCP, AWS, Hetzner, Cloudflare}
\skillgroup{Linux}{Ubuntu, Debian, Red Hat, Rocky Linux, CentOS, FreeBSD}
\skillgroup{Virtualization}{Proxmox, KVM, bare-metal, Vagrant}
\skillgroup{Containers}{Kubernetes (5+ yrs), Docker, Podman, Helm}
\skillgroup{IaC}{Terraform, Puppet, Ansible, HashiCorp Packer}
\skillgroup{Networking}{OpenVPN, WireGuard, NetBird, DNS, BGP}
\skillgroup{Databases}{PostgreSQL, MySQL, Redis, MongoDB, Cassandra}

\sidesection{CI/CD \& Reliability}
\skillgroup{Pipelines}{Jenkins, GitLab CI, GitHub Actions, CircleCI, ArgoCD}
\skillgroup{Proxy / LB}{HAProxy, Nginx, Traefik, Squid Proxy}
\skillgroup{Security}{HashiCorp Vault, Keycloak, SSO, OAuth, JWT}

\sidesection{Observability}
\skillgroup{Metrics / Tracing}{Prometheus, OpenTelemetry, Grafana, Loki, Tempo}
\skillgroup{Stacks}{ELK, Datadog, Wavefront}

\sidesection{AI \& LLM}
\skillgroup{Models}{Claude (Opus, Sonnet, Haiku), GPT-4, Llama, DeepSeek}
\skillgroup{Tooling}{Claude Code, Anthropic Agent SDK, Cursor, GitHub Copilot}
\skillgroup{Integration}{Anthropic API, OpenAI API, Ollama, prompt caching, tool use}

\sidesection{Frameworks}
\skillgroup{Python}{Django, Flask, DRF, SQLAlchemy, Celery, Scrapy}
\skillgroup{JS \& Go}{Next.js, Vue.js, Backbone.js, Socket.io, Gorilla Mux}
\skillgroup{Misc}{Stripe, rrweb, WebSockets, Jitsi}

\sidesection{Education}
\skillgroup{Tehran University}{Bachelor of Software Engineering. 2009 -- Incomplete.}
\skillgroup{NODET}{Mathematics track. 2002 -- 2009.}

\sidesection{Community}
{\fontsize{8.5}{11}\selectfont\color{ink}
{\color{c2}\bfseries TehranLUG.} Co-Founder, 2009 -- present.\par\vspace{2pt}
{\color{c2}\bfseries IrPycon.} Founder of the Iranian Python community, 2014 -- present.\par\vspace{2pt}
{\color{c2}\bfseries SalamDonya.} Editor-in-chief of Iran's first free software magazine, 2016 -- 2017.\par\vspace{2pt}
{\color{c2}\bfseries ZConf.} Presenter and editorial board, 2011 -- 2016.\par\vspace{2pt}
{\color{c2}\bfseries Open source.} 38 public repos including
\href{https://github.com/efazati/i3buntu}{\textit{\color{c3}i3buntu}} (57\,$\star$),
\href{https://github.com/efazati/samwise}{\textit{\color{c3}samwise}},
\href{https://github.com/efazati/satl}{\textit{\color{c3}satl}}.
}

\vfill
\vspace{18pt}
{\color{rule}\rule{\linewidth}{0.3pt}}\\[3pt]
{\color{warm}\bfseries\fontsize{7.5}{9}\selectfont RESUME V2.1.0}\hfill{\color{mutedLight}\fontsize{7.5}{9}\selectfont\today}

\switchcolumn

% ----- RIGHT MAIN COLUMN -----

\cvsection{Experience}
\fontsize{9.5}{11.5}\selectfont

\role{EasyEnv}{Co-Founder, at Donedeploy}{Remote, Ireland}{Jan 2023 -- Present}
Hiring platform that interviews engineers on real production Linux. Candidates use AI; teams watch every keystroke. \href{https://easyenv.io}{\color{c3}EasyEnv} is Donedeploy's flagship product.
\techline{Kubernetes, Terraform, AWS, GCP, Python, Next.js, Anthropic API, NetBird}
\begin{itemize}
  \item Built ephemeral VMs, session recording, multi-tenancy, OAuth/JWT, recipe-based machine config.
  \item 58+ Ansible recipes for Kubernetes, ELK, monitoring, broken-on-purpose interview challenges.
  \item Live collab: shared terminals, port-view proxy, Jitsi, rrweb replay with custom compression.
  \item AI features via Claude + Anthropic Agent SDK. Engineered on Claude Code.
  \item AI-era hiring positioning: candidates use AI, teams watch every keystroke.
\end{itemize}

\role{Royal Bank of Canada}{Principal DevOps Engineer, via Manakau}{Remote, Ireland}{Nov 2022 -- Sep 2023}
Led 5 engineers building an internal developer platform so quant developers could ship to production without touching Jenkins, Kubernetes, or HTTP plumbing themselves.
\techline{AWS, Kubernetes, OpenShift, OpenTelemetry, Python, Jenkins, Prometheus}
\begin{itemize}
  \item Introduced OpenTelemetry across services for vendor-agnostic observability.
  \item Shipped a full developer environment with all required languages, tooling, and project scaffolding pre-wired.
  \item Built custom Linux containers on OpenShift as Jenkins agents; deployed and operated the Prometheus cluster.
\end{itemize}

\roleSimple{Clover, Fiserv}{Nenagh, Ireland \, \,$\cdot$\, \, Dec 2020 -- Nov 2022}
\noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
  {\color{warm}\bfseries EMEA DevOps Engineering Manager} & {\color{muted}\fontsize{8.5}{10}\selectfont May 2022 -- Nov 2022} \\
\end{tabular*}\par
Managed 8 engineers and the service architecture they owned.
\techline{GCP, Kubernetes, Puppet, Terraform, Go, Jenkins, Vault}
\begin{itemize}
  \item Introduced an agile intake model (run-the-business vs. project work) to stabilize infrastructure delivery.
  \item Redesigned Jenkins with autoscaling, HA, and a hardened security model.
\end{itemize}
\noindent\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
  {\color{warm}\bfseries Staff DevOps Engineer} & {\color{muted}\fontsize{8.5}{10}\selectfont Dec 2020 -- May 2022} \\
\end{tabular*}\par
Owned reliability, performance, and capacity for Clover's products end-to-end.
\begin{itemize}
  \item Built outbound-request caching with Squid plus health-checked traffic rotation, written in Go.
  \item Stood up ephemeral test environments alongside Dev Integration, Staging, and QA tiers.
  \item Unified CI/CD across 200+ projects with a cleaner SCM strategy.
\end{itemize}

\role{Cainthus}{Senior DevOps Engineer}{Dublin, Ireland}{Sep 2018 -- Dec 2020}
Built a hybrid cloud + edge platform so every team could ship autonomously.
\techline{Kubernetes, AWS, Ansible, Terraform, Go, Python, NVIDIA Jetson, Raspberry Pi}
\begin{itemize}
  \item Wrote a Kubernetes + AWS wrapper (API and CLI) with ACL and integrated CI/CD.
  \item Built the Kubernetes installation pipeline end-to-end as code.
  \item Operated a 100+ node distributed Kubernetes cluster spanning x86 and ARM.
  \item Automated OpenVPN deployment, monitoring, central user management, and HA.
\end{itemize}

\role{Noavaran Saramad Sharif}{DevOps Tech Lead}{Tehran, Iran}{Jul 2017 -- Sep 2018}
Owned architecture, schema design, and CI/CD across the engineering team.
\techline{Python, Django, Vue.js, Kubernetes, PostgreSQL, ELK}
\begin{itemize}
  \item Shipped \textit{Mobank wallet} (\href{http://mobank.co}{\color{c3}mobank.co}), a payment system integrated with government banks.
  \item Designed an end-to-end encryption layer handling MITM, key exchange, and rotation.
  \item Customized Open edX as the foundation for a local e-learning platform.
\end{itemize}

\role{AEC \, \,{\color{muted}\mdseries\fontsize{9}{11}\selectfont (formerly Cvas)}}{Co-Founder, Software Engineering Director}{Tehran, Iran}{Jan 2013 -- Jul 2017}
Co-founded \textbf{\color{accent}Cvas} in 2013; acquired by AEC in 2015 and stayed on as Engineering Director. Led a 30+ engineer team, drove architecture, shipped the most complex modules.
\techline{Python, Django, MongoDB, Cassandra, Go, Redis, Celery, RabbitMQ}
\begin{itemize}
  \item \href{http://www.argus-nms.com}{\color{c2}\textbf{ARGUS}}. Network and sensor monitoring at MTN Irancell (1M sensors per second).
  \item \href{https://www.nanodlp.com}{\color{c2}\textbf{nanoDLP}}. First Iranian 3D printer software running on Raspberry Pi.
  \item \href{http://mazanex.com}{\color{c2}\textbf{Mazanex}}. Currency, gold, and stock market monitoring with 6M daily visits.
  \item \href{http://bab.ir}{\color{c2}\textbf{BAB}}. Marketplace for 8K+ Iranian shops; also powered \textit{Itzar} gold market.
  \item Wikipedia analysis with Word2Vec and graph relations, TF-IDF news summarization, event-detection news aggregator.
  \item Operated 30+ servers covering Nginx, uWSGI, GitLab CI, monitoring, backup, and disaster recovery.
\end{itemize}

\roleSimple{Earlier roles}{Tehran \, \,$\cdot$\, \, 2007 -- 2013}
\vspace{2pt}
{\color{c2}\textbf{Bayan.}} \meta{Senior Software Engineer, 2010 -- 2013.} Designed and shipped \textit{Blog.ir}, \textit{Bayanbox} (file sharing), \textit{Hod} (email), and Bayan SSO from scratch on Python, Django, and MongoDB.\\[7pt]
{\color{c2}\textbf{Sepehr Andisheh Javan.}} \meta{Software Engineer, 2010.} SCORM LMS, web-based ERP, Tehran Short Film Festival site.\\[7pt]
{\color{c2}\textbf{Farzan Institute.}} \meta{Software Engineer, 2009 -- 2010.} Moodle customizations: Farasa, Sanje, Faradata.\\[7pt]
{\color{c2}\textbf{Freelance.}} \meta{2007 -- 2010.} 50+ websites and 30+ MVPs shipped for SMEs.

\end{paracol}

\end{document}
